Typed Functional Genetic Programming

### 2013-08-01 tex/thesis.tex
čtvrtek 7:21

Aplikace: například v oboru počítačových her, kde nám často jde o
zajímavé nelineární chování by se tento přístup k využití typovaného funkcionálního
programování dal využít.

Předvedený postup by taky ohlo být možné použít na

%\section{Results summary}

@@

\section{Genetic Programming with Polymorphic Types and Higher-Order Functions}
by Franck Binard and Amy Felty

\begin{todo}
 & dopsat nebo vyhodit
\end{todo}

@@

>>>>

~\\
\includegraphics[scale=0.33]{fly/4.png}

Application of this kind of approach is for example 
computer games design where non-linearity and adaptability
to players actions are highly appreciated. 
Also games are not tight by some fixed specification
so this approach might be very appropriate in this industry.

~\\[1em]

\includegraphics[scale=0.35]{fly/5.png}

@@

%\section{Genetic Programming with Polymorphic Types and Higher-Order Functions}
%by Franck Binard and Amy Felty
%
%\begin{todo}
% & dopsat nebo vyhodit
%\end{todo}

@@

\appendix
\chapter{First Appendix}

abc
